---
title: "myvignette1"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{myvignette1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(StatComp22037)
```



The two-parameter log-logistic model(2PLM) corresponds to the model function:

$f(x)=\dfrac{1}{1+exp[b{\log(x)-\log(\phi_3)}]}$
or in another parameterization

$f(x)=c+\dfrac{d-c}{1+exp[b{\log(x)-\phi_3}]}$

The three-parameter log-logistic model(3PLM) corresponds to the model function:

$f(x)=\dfrac{d}{1+exp[b{\log(x)-\log(\phi_3)}]}$
or in another parameterization

$f(x)=\dfrac{d}{1+exp[b{\log(x)-\phi_3}]}$

The four-parameter log-logistic model(4PLM) corresponds to the model function:

$f(x)=c+\dfrac{d-c}{1+exp[b{\log(x)-\log(\phi_3)}]}$
or in another parameterization

$f(x)=c+\dfrac{d-c}{1+exp[b{\log(x)-\phi_3}]}$

The five-parameter log-logistic model(5PLM) corresponds to the model function:

$f(x)=c+\dfrac{d-c}{(1+exp[b{\log(x)-\log(\phi_3)}])^{f}}$
or in another parameterization

$f(x)=c+\dfrac{d-c}{(1+exp[b{\log(x)-\phi_3}])^f}$.

